An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-10 ex3/paper/paper.tex
Finish some citation issue

Many explainability methods proposed recently are local and thus provide an explaination for a particular data sample \cite{shapley_value_1953,lundberg_unified_2017,dhurandhar_model_nodate,ribeiro_why_2016}. However, for the particular problem of network traffic due to the high number of flows and characteristics of data, analyzing individual samples is of low interest. Thus explainability methods presented in this paper aim to understand a model by analyzing which features are important, at which time step they are important and which feature values lead to classification as attack.

>>>>

Many explainability methods proposed recently are local and thus provide an explaination for a particular data sample \cite{shapley_value_1953,lundberg_unified_2017,dhurandhar_model_2018,ribeiro_why_2016}. However, for the particular problem of network traffic due to the high number of flows and characteristics of data, analyzing individual samples is of low interest. Thus explainability methods presented in this paper aim to understand a model by analyzing which features are important, at which time step they are important and which feature values lead to classification as attack.
